Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-03-11 Thesis/chapter/07-outlook.tex
first complete draft

%\todo{freewriting:} 
%what did i want to do? 
The goal of this work was to find a sol-gel doctor blading process resulting in a insulating zirconium ceramic on top of steel.
This structure then can be used as substrate for thin layer photo voltaics. 
The ceramic needs to be homoegeneous and defect free in order to insulate properly.
%what was done? 
A suitable recipe was found\cite{Hu2016} and the process variables were optimized via \gls{emma}. 
The recipe was improved by increasing its stability. 
The best parameters found by the emma optimization were 
$c_{zr}=2$, $\lambda=10$, $v_{DB}=10$, $T_{DB}=40$, $v_{cal}=120$ and $T_{cal}=300$.
%\todo{$T_{cal}=300$}. 
%welche methoden wurden dafür verwendet? 
After optimzation the data was analyzed with further machine learning methods like kernel ridge regression, support vector regression and linear regression. 
The comparisson of methods showed that \gls{emma} performed well on predicting the correlation between conductance and process variables. 
%was wurde herausgefunden? 
A strong correlation of calcination temperature and conductance in the bereich of 300--400\oc{}. 
%was kann noch herausgefundne werden und wie? 
Next steps include to investigate if the correlation of condactance and calcination temperature are statistically significant or due to small sample size. 
The aging process could be examined via infra red spectroscopy. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\iffalse
was kann noch veraendert werden? 
humidity 
solution age
vdb and tdb on g and phd 
Tcal on g and phd 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

>>>>

%\todo{freewriting:} 
%what did i want to do? 
The goal of this work was to find a sol-gel doctor blading process resulting in a insulating zirconium ceramic on top of steel.
This structure then can be used as substrate for thin layer photovoltaics. 
The ceramic needs to be homogeneous and defect free in order to insulate properly.
%what was done? 
A suitable recipe was found\cite{Hu2016} and the process variables were optimized via \gls{emma}. 
The recipe was improved by increasing its stability. 
The best parameters found by the \gls{emma} optimization were 
$c_{zr}=2$, $\lambda=10$, $v_{DB}=10$, $T_{DB}=40$, $v_{cal}=120$ and $T_{cal}=300$.
%\todo{$T_{cal}=300$}. 
%welche methoden wurden dafür verwendet? 
After optimization, the data was analyzed with further machine learning methods like kernel ridge regression, support vector regression and linear regression. 
The comparison of methods showed that \gls{emma} performed well on identifying the important correlation between conductance and process variables. 
%was wurde herausgefunden? 
A strong correlation of calcination temperature and conductance in the range of 300--500\oc{} has been detected.
Furthermore, the layer count has been verified as an important factor. 
%was kann noch herausgefundne werden und wie? 
Next steps include to investigate if the correlation of conductance and calcination temperature are statistically significant or due to small sample size. 
The aging process could be examined via infra red spectroscopy. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\iffalse
was kann noch veraendert werden? 
humidity 
solution age
vdb and tdb on g and phd 
Tcal on g and phd 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
